---
title: "Gov 50 Final Project"
author: "Linda"
date: "2022-12-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
wvs <- read_csv("WVS_Cross-National_Wave_7_csv_v4_0.csv")
wvs
```

```{r}
wvs1 <- wvs |>
  select(A_YEAR, A_STUDY, B_COUNTRY, B_COUNTRY_ALPHA, D_INTERVIEW, L_INTERVIEWER_NUMBER, Q275, Q288, Q199:Q212)
wvs1
```

```{r}
wvs2 <- wvs1 |>
  rename(education = Q275,
         income = Q288,
         political_interest = Q199,
         discuss_w_friends = Q200,
         newspaper = Q201,
         tv = Q202,
         radio = Q203,
         phone = Q204,
         email = Q205,
         internet = Q206,
         social_media = Q207,
         informal_talks = Q208,
         petition = Q209,
         boycotts = Q210,
         demonstrations = Q211,
         strikes = Q212)
wvs2
```


```{r}
library(countrycode)
wvs3 <- wvs2 |>
  mutate(Country = countrycode(B_COUNTRY_ALPHA, origin = "iso3c", destination = "country.name")) |>
  select(!c(B_COUNTRY, B_COUNTRY_ALPHA))
wvs3
```


```{r}
wvs_data <- wvs3 |>
  group_by(Country) |>
  summarize(education = mean(education, na.rm = TRUE) / 8,
         income = mean(income, na.rm = TRUE) / 10,
         political_interest = mean(political_interest, na.rm = TRUE) / 4,
         discuss_w_friends = mean(discuss_w_friends, na.rm = TRUE) / 3,
         newspaper = mean(newspaper, na.rm = TRUE) / 5,
         tv = mean(tv, na.rm = TRUE) / 5,
         radio = mean(radio, na.rm = TRUE) / 5,
         phone = mean(phone, na.rm = TRUE) / 5,
         email = mean(email, na.rm = TRUE) / 5,
         internet = mean(internet, na.rm = TRUE) / 5,
         social_media = mean(social_media, na.rm = TRUE) / 5,
         informal_talks = mean(informal_talks, na.rm = TRUE) / 5,
         petition = mean(petition, na.rm = TRUE) / 3,
         boycotts = mean(boycotts, na.rm = TRUE) / 3,
         demonstrations = mean(demonstrations, na.rm = TRUE) / 3,
         strikes = mean(strikes, na.rm = TRUE) / 3
            )
wvs_data
```


```{r}
freedom_house <- read_csv("Freedom of the Press 2017.csv")
freedom_house <- freedom_house |>
  rename(total_score = "Total Score") |>
  mutate(total_score = as.integer(total_score)) |>
  group_by(Country) |>
  summarize(media_freedom_score = total_score)
freedom_house
```


```{r}
freedom <- wvs_data |>
  inner_join(freedom_house) |>
  select(Country, media_freedom_score, education:strikes)
freedom
```

```{r}
media_petition <- freedom |>
  ggplot(mapping = aes(x = media_freedom_score,
         y = petition)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "indianred1", size = 1.5) +
  coord_cartesian(xlim = c(0, 100), ylim = c(0, 1)) +
  labs(title = "Media Freedom and Willingness to Join Petition",
       x = "Media Freedom Score",
       y = "Average Willingness to Join Petition")
media_petition

media_boycotts <-freedom |>
  ggplot(mapping = aes(x = media_freedom_score,
         y = boycotts)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "indianred1", size = 1.5) +
  coord_cartesian(xlim = c(0, 100), ylim = c(0, 1)) +
  labs(title = "Media Freedom and Willingness to Participate in Boycotts",
       x = "Media Freedom Score",
       y = "Average Willingness to Participate in Boycotts")
media_boycotts

media_demonstrations <- freedom |>
  ggplot(mapping = aes(x = media_freedom_score,
         y = demonstrations)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "indianred1", size = 1.5) +
  coord_cartesian(xlim = c(0, 100), ylim = c(0, 1)) +
  labs(title = "Media Freedom and Willingness to Attend Lawful Demonstrations",
       x = "Media Freedom Score",
       y = "Average Willingness to Attend Lawful Demonstrations")
media_demonstrations

media_strikes <- freedom |>
  ggplot(mapping = aes(x = media_freedom_score,
         y = strikes)) +
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE, color = "indianred1", size = 1.5) +
  coord_cartesian(xlim = c(0, 100), ylim = c(0, 1)) +
  labs(title = "Media Freedom and Willingness to Join Unofficial Strikes",
       x = "Media Freedom Score",
       y = "Average Willingness to Join Unofficial Strikes")
media_strikes
```


```{r}
library(infer)
library(broom)
fit_petition <- lm(petition ~ media_freedom_score + education + income + political_interest, data = freedom)

library(broom)

var_labels <- c(
    "(Intercept)" = "Intercept",
    "media_freedom_score" = "Media Freedom Score",
    "education" = "Education",
    "income" = "Income",
    "political_interest" = "Political Interest"
)

modelsummary::modelsummary(fit_petition,
                             statistic = c("s.e. = {std.error}",
               "p = {p.value}"),
coef_map = var_labels,
gof_map = c("nobs", "r.squared", "adj.r.squared"))
```


```{r}
fit_boycotts <- lm(boycotts ~ media_freedom_score + education + income + political_interest, data = freedom)

library(broom)

var_labels <- c(
    "(Intercept)" = "Intercept",
    "media_freedom_score" = "Media Freedom Score",
    "education" = "Education",
    "income" = "Income",
    "political_interest" = "Political Interest"
)

modelsummary::modelsummary(fit_boycotts,
                             statistic = c("s.e. = {std.error}",
               "p = {p.value}"),
coef_map = var_labels,
gof_map = c("nobs", "r.squared", "adj.r.squared"))
```


```{r}
fit_demonstrations <- lm(demonstrations ~ media_freedom_score + education + income + political_interest, data = freedom)

library(broom)

var_labels <- c(
    "(Intercept)" = "Intercept",
    "media_freedom_score" = "Media Freedom Score",
    "education" = "Education",
    "income" = "Income",
    "political_interest" = "Political Interest"
)

modelsummary::modelsummary(fit_demonstrations,
                             statistic = c("s.e. = {std.error}",
               "p = {p.value}"),
coef_map = var_labels,
gof_map = c("nobs", "r.squared", "adj.r.squared"))
```


```{r}
fit_strikes <- lm(strikes ~ media_freedom_score + education + income + political_interest, data = freedom)

library(broom)

var_labels <- c(
    "(Intercept)" = "Intercept",
    "media_freedom_score" = "Media Freedom Score",
    "education" = "Education",
    "income" = "Income",
    "political_interest" = "Political Interest"
)

modelsummary::modelsummary(fit_strikes,
                             statistic = c("s.e. = {std.error}",
               "p = {p.value}"),
coef_map = var_labels,
gof_map = c("nobs", "r.squared", "adj.r.squared"))
```


## Cleaning up data


## Introduction
Research question:
1-2 paragraphs

## Data and research design
Description of data
description of research design: cross-sectional
a plot that summarizes the dependent variable (both a table and a histogram? in ascendency)
a couple of paragraphs

## Data Analysis
Multiple regression
Explanation and analysis (in plain English) the main coefficient of interest in your regression, comment on the statistical significance of the estimated coefficient, and  say whether or not you believe the coefficient to represent a causal effect.)

## Conclusion
recap of results
discussions of limitations of study
how to improve the study in the future
1 paragraph